|

### 2024-07-30 manuscript/paper.Rmd
rearranging author order

---
title: |
  |  \Large Increased sexual dimorphism evolves in a fossil stickleback following ecological release from fish piscivores
author: | 
  | \large Allison Ozark$^{1,*}$, Matthew Stuart$^{2,3,*}$, Raheyma Siddiqui$^1$, Akhil Ghosh$^{2,3}$
  | \large Samantha Swank$^1$, Michael A. Bell$^4$, Gregory J. Matthews$^{2,3}$, and Yoel E. Stuart$^{1,+}$ 
  | \vspace{-1.1mm}
  | \large $^1$ Department of Biology, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  | \large $^2$ Department of Mathematics and Statistics, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  | \large $^3$ Center for Data Science and Consulting, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  | \large $^4$ University of California Museum of Paleontology, Berkeley, CA, USA \vspace{-1.1mm}
  | \large $^*$ Equal contribution \vspace{-1.1mm}
  | \large $^+$ Corresponding: ystuart@luc.edu \vspace{-1.1mm}
abstract: |
  | Everyone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---

>>>>

---
title: |
  |  \Large Increased sexual dimorphism evolves in a fossil stickleback following ecological release from fish piscivores
author: | 
  | \large Matthew Stuart$^{1,2}$, Allison Ozark$^{3}$, Raheyma Siddiqui$^3$, Akhil Ghosh$^{1,2}$
  | \large Samantha Swank$^3$, Michael A. Bell$^4$, Gregory J. Matthews$^{1,2}$, and Yoel E. Stuart$^{3,+}$ 
  | \vspace{-1.1mm}
  | \large $^1$ Department of Mathematics and Statistics, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  | \large $^2$ Center for Data Science and Consulting, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  | \large $^3$ Department of Biology, Loyola University Chicago, Chicago, IL, USA \vspace{-1.1mm}
  | \large $^4$ University of California Museum of Paleontology, Berkeley, CA, USA \vspace{-1.1mm}
  | \large $^+$ Corresponding: ystuart@luc.edu \vspace{-1.1mm}
abstract: |
  | Everyone loves the stickle \vspace{2mm}
  | *Keywords*: Stickle
bibliography: references.bib
fontsize: 12pt
link-citations: true
linkcolor: cyan
urlcolor: cyan
output:
  pdf_document:
    df_print: kable
    number_sections: true
    keep_tex: true
header-includes:
 \usepackage{setspace}
 \setstretch{1.15}
 \usepackage{float}
 \floatplacement{figure}{t}
---
